Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-24 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
typos and tables

\from{Nick}{TODO: Update Figure \ref{fig:analogy} with correct representation for current version.}

@@

% all images in a single figure -- pretty ugly and a waste of space
% \begin{figure*}[t]
%   \includegraphics[width=\textwidth]{images/worked-example.png}
%   \caption{\textbf{TODO}}
%   \label{fig:rooms-and-pic}
% \end{figure*}

\begin{figure}
  \includegraphics[width=\columnwidth]{images/worked-example-rooms.png}
  \caption{Maps of 2 real classrooms generated by our system, plus an expert-annotated CDSR (orange, top image), subject-annotated CDSR (red, bottom image) and a CDSR transferred by analogy (green bottom image). The classroom used to generate the top classroom is pictured in Figure~\ref{fig:ug40}}
  \label{fig:rooms}
\end{figure}

>>>>

\from{Nick}{Kate, please update figure caption, plus descriptive paragraph below}

@@

\begin{figure}
	% can swap these 2 lines for different presentations - and colours!
 \includegraphics[width=\columnwidth]{images/worked-example.png}
  % \includegraphics[width=\columnwidth]{images/worked-example-rooms.png}
  \caption{Maps of 2 real classrooms generated by our system, plus an expert-annotated CDSR (red, top image), subject-annotated CDSR (blue, bottom image) and a (smaller) CDSR transferred by analogy (green bottom image). The classroom used to generate the bottom classroom is pictured in Figure~\ref{fig:ug40}.}
  \label{fig:rooms}
\end{figure}
